---
title: "Untitled"
author: "Jaehwan Lim"
date: "January 13, 2019"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(janitor)
library(stringr)

recent_grads <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-10-16/recent-grads.csv") %>% clean_names()

major_processed <- recent_grads %>% 
  arrange(desc(median)) %>%
  mutate(major = str_to_title(major), 
         major = fct_reorder(major, median)) 

theme_set(theme_light())
```

## What are the most common major categories?

```{r}
by_major_category %>% 
  mutate(major_category = fct_reorder(major_category, total)) %>%
  gather(gender, number, men, women) %>% 
  ggplot(aes(major_category, number, fill = gender)) + 
  geom_col() +
  coord_flip() +
  scale_y_continuous(labels = scales::comma_format()) + 
  labs(x = "", 
       y = "Total number of graduates", 
       major_category = "") 
  
```

## What are the most common *majors*? (since there are 173 majors, we can't show them all)

```{r}
major_processed %>% 
  arrange(desc(total)) %>% 
  head(20) %>% 
  mutate(major = fct_reorder(major, total)) %>% 
  ggplot(aes(major, total, fill = major)) + 
  geom_col() +
  coord_flip() + 
  scale_y_continuous(labels = scales::comma_format()) +
  theme(legend.position = "none") +
  labs(x = "Top 20 most common majors", 
       y = "Total of graduates surveyed")
 
```

## What categories of majors make more moeny than others?

```{r}
recent_grads %>%
  mutate(major_category = fct_reorder(major_category, median)) %>% 
  ggplot(aes(major_category, median, fill = major_category)) + 
  geom_boxplot() + 
  coord_flip() + 
  scale_y_continuous(labels = scales::dollar_format()) +
  expand_limits(y = 0) +
  theme(legend.position = "none")
```

## What are the highest earning majors?

```{r}
major_processed <- recent_grads %>% 
  arrange(desc(median)) %>% 
  select(major, major_category, median, p25th, p75th, sample_size) %>% 
  mutate(major = str_to_title(major), 
         major = fct_reorder(major, median)) 

major_processed %>% 
  filter(sample_size >= 100) %>% 
  head(20) %>% 
  ggplot(aes(major, median, color = major_category)) + 
  geom_point() + 
## show interval 
  geom_errorbar(aes(ymin = p25th, ymax = p75th)) + 
  coord_flip() + 
  scale_y_continuous(labels = scales::dollar_format()) +
## set the y limit to 0
  expand_limits(y = 0) + 
  labs(title = "What are the highest-earning majors?", 
       subtitle = "Top 20 majors with at least 100 graduates surveyed", 
       y = "Median graduate salary")

```

## What are the lowest earning majors?

```{r}
major_processed %>% 
  tail(20) %>% 
  ggplot(aes(major, median, color = major_category)) + 
  geom_point() + 
## show interval 
  geom_errorbar(aes(ymin = p25th, ymax = p75th)) + 
  coord_flip() + 
  scale_y_continuous(labels = scales::dollar_format()) +
## set the y limit to 0
  expand_limits(y = 0)

```

### Checking the sample size

```{r}
major_processed %>%
  ggplot(aes(sample_size, median)) +
  geom_point() +
  geom_text(aes(label = major), check_overlap = T, vjust = 1, hjust = 1) +
  scale_x_log10()

```

## How does gender ratio relate to earnings?

```{r}
library(ggrepel)

major_processed %>% 
  arrange(desc(total)) %>% 
  head(20) %>% 
  ## tidying the data
  gather(gender, number, men, women) %>% 
  mutate(major = fct_reorder(major, total)) %>% 
  ggplot(aes(major, number, fill = gender)) + 
  geom_col() + 
  coord_flip()

major_processed %>% 
  filter(!is.na(total)) %>% 
  group_by(major_category) %>% 
  summarize(total = sum(total), 
            men = sum(men), 
            women = sum(women), 
            median_salary = sum(median * sample_size) / sum(sample_size)) %>% 
  mutate(share_women = women / total) %>% 
  ggplot(aes(share_women, median_salary)) + 
  geom_point() +
  geom_text_repel(aes(label = major_category)) + 
  geom_smooth(method = "lm") +
  expand_limits(y = 0) 
  
```


# I'll also be aggregating by category

```{r by_major_category}

by_major_category <- major_processed %>% 
  filter(!is.na(total)) %>% 
  group_by(major_category) %>% 
  summarize(total = sum(total), 
            men = sum(men), 
            women = sum(women), 
            median_salary = sum(median * sample_size) / sum(sample_size)) %>% 
  mutate(share_women = women / total) %>% 
  arrange(desc(share_women))

```

```{r}
library(plotly)

g <- major_processed %>% 
  mutate(major_category = fct_lump(major_category, 4)) %>% 
  ggplot(aes(share_women, median, color = major_category, size = sample_size, labels = major)) +
  geom_point() + 
  geom_smooth(aes(group = 1), method = "lm") +
  scale_x_continuous(labels = scales::percent_format()) +
  scale_y_continuous(labels = scales::dollar_format()) +
  expand_limits(y = 0)

ggplotly(g)

```

```{r}
major_processed %>% 
  select(major, total, share_women, sample_size, median) %>% 
  lm(median ~ share_women, data = ., weights = sample_size) %>% 
  summary()
```

```{r}
library(broom)

major_processed %>% 
  select(major, major_category, total, share_women, sample_size, median) %>%
  add_count(major_category) %>%
  filter(n >= 10) %>%
  nest(-major_category) %>% 
  mutate(model = map(data, ~ lm(median ~ share_women, data = ., weights = sample_size)), 
         tidied = map(model, tidy)) %>%
  unnest(tidied) %>% 
  filter(term == "share_women") %>% 
  arrange(estimate) %>% 
  ## adjust p-value using fdr
  mutate(fdr = p.adjust(p.value, method = "fdr"))

```

```{r}
recent_grads %>% 
  filter(sample_size >= 100) %>% 
  mutate(IQR = p75th - p25th) %>% 
  arrange(desc(IQR)) %>% 
  View()

```

# Future work
  * Examining umemployment and fraction taking a job requiring a college degree
  * Examining IQR
  
```{r}
knitr::knit_exit()
```

```{r}
recent_grads %>%
  group_by(major_category) %>% 
  summarize(median_median = median(median)) %>% 
  mutate(major_category = fct_reorder(major_category, median_median)) %>% 
  ggplot(aes(major_category, median_median)) + 
  geom_col() + 
  coord_flip() + 
  scale_y_continuous(labels = scales::dollar_format())
```
